%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Modified by : Federico Lenzi
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{scrextend}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubheadingDescription}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{1pt}
	\small#5\vspace{-4pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{--}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={}, leftmargin=10pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItemDescpritionStart}{\begin{itemize}}
\newcommand{\resumeItemDescpritionEnd}{\end{itemize}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Federico Lenzi} & Email : \href{mailto:federicolenzi@gmail.com}{federicolenzi@gmail.com}
  
  \\
  \href{https://www.linkedin.com/in/flenzi/}{linkedin.com/in/flenzi} & Mobile : +34 695 31 63 64 \\
\end{tabular*}


%-----------ABOUT-----------------
\section{About}
\small {
Dynamic Software Engineer with experience delivering innovative software solutions as a key developer, team lead, and scrum master. A passion for software design and back-end development drives me to consistently deliver high-quality results that meet client needs and exceed expectations.


\vspace{2mm} %5mm vertical space

With a focus on scalability and performance, I have a proven track record of delivering projects on-time and within budget while continuously striving to improve processes and increase efficiency. My exceptional collaboration skills and proactive approach have earned me recognition as a valuable team player, always willing to lend a hand and contribute to finding the best solution.

\vspace{2mm} %5mm vertical space

As a lifelong learner, I am eager to work in a dynamic environment where growth and development are promoted. I am confident in my ability to lead cross-functional teams and deliver results that drive business success.

}
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BestSecret}{Malaga, Spain}
      {Senior Software Engineer}{Apr 2022 -- Present}
      
      \resumeItemListStart
        \resumeItem
          {Webshop}
          {Working on a customer engagement team in charge of the home page and the games.}
           \resumeItemDescpritionStart
             \item Techs: Java, Kotlin, Hybris, Vue.js, GraphQL, Git, Microservices, Spring Boot, Redis, PostgreSQL, MongoDB, Prometheus, Docker, Kubernetes, Azure
           \resumeItemDescpritionEnd
      \resumeItemListEnd  
   
    \resumeSubheading    
      {Epam}{Malaga, Spain}
      {Lead Software Engineer}{Feb 2019 -- Apr 2022}
      
      \resumeItemListStart
        \resumeItem
          {Iron Mountain}
          {Worked as a full stack developer on Cognitive Workbench, a highly customizable tool to extract, process and transform information from digital documents.}
           \resumeItemDescpritionStart
             \item Techs: Java, Angular, TypeScript, Git, Microservices, Spring Boot, Spring Data, Redis, PostgreSQL, MongoDB, Prometheus, Docker, Kubernetes, Google Kubernetes Engine (GKE), Google Cloud Platform (GCP) 
           \resumeItemDescpritionEnd
        \resumeItem
          {Corelogic}
          {Played a key role as a developer in the creation and upkeep of services that generate mortgages and real estate reports for multiple applications. Coordinating with cross-functional teams to drive new releases, resolve issues, and conduct investigations while ensuring smooth operation of these critical services.}
           \resumeItemDescpritionStart
             \item Techs: Java, various relational DBs, Redis, Pivotal Cloud Foundry
           \resumeItemDescpritionEnd
      \resumeItemListEnd   
      
    \resumeSubheading
      {Infor}{Buenos Aires, Argentina}
      {Senior Software Engineer}{May 2014 -- Jan 2019}

      \resumeItemListStart
        \resumeItem
          {Connect}
          {Developed a highly customizable middleware to seamlessly integrate internal and third-party services, culminating in a successful migration from a monolithic application to a microservices architecture.}
           \resumeItemDescpritionStart
             \item Techs: Java, Spring Cloud ecosystem, Swagger, Docker, AWS
           \resumeItemDescpritionEnd
        \resumeItem
          {Data Import}
          {Developed a data ingestion application for stores, which involved rewriting the existing approach to create a more scalable and efficient solution. The resulting application is capable of handling large volumes of data with ease and has greatly improved the data ingestion process.}
			\resumeItemDescpritionStart
             \item Techs: Java, Spring Batch, Postgres, Cassandra/Solr, Apache Camel
           \resumeItemDescpritionEnd
      \resumeItemListEnd      
      
    \resumeSubheading
      {Devspark}{Tandil, Argentina}
      {Software Engineer}{Jul 2012 -- May 2014}
    \resumeSubheading
      {Globant}{Tandil, Argentina}
      {Quality Software Engineer}{May 2011 -- Jun 2012}
  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java, Kotlin, Bash, Python, Javascript}
    }   
    \item{
       \textbf{Frameworks/Tools}{: Spring (IOC, MVC, Boot, Data), Hibernate, Apache Camel, Kafka, Angular, Vue.js}
    }       
    \item{
       \textbf{Databases}{: Postgres, MySQL, Cassandra, MongoDB, Solr, Redis}
    }
    \item{
       \textbf{Cloud}{: Azure, GCP, AWS, Pivotal Cloud Foundry}
    }
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingDescription
      {UNICEN}{Tandil, Argentina}
      {Bachelor of System Engineering}{2006 -- 2011}
      {Relevant courses: Service Oriented Computing, Introduction to Grid Computing, Information Retrieval, Agile Methodologies, Aspect Oriented Programming, Web Tools, Evolutionary computation.}
  \resumeSubHeadingListEnd


\end{document}
